Jeff Goldsmith

### 2019-03-05 papers.Rmd
add a paper
update directory name ("Downloads" -> "resources")

@@

D. Backenroth<sup>&#8225;</sup>, **J. Goldsmith**, M. D. Harran, J. C. Cortes, J. W. Krakauer, and T. Kitago (2018+).
Modeling motor learning using heteroskedastic functional principal components analysis.
<i> Journal of the American Statistical Association, </i> 
accepted.
[[PDF](Downloads/HetFCPA.pdf)]

@@

**J. Goldsmith**, X. Liu<sup>&#8225;</sup>, J. S. Jacobson, A. Rundle (2016).
New insights into activity patterns in children, found using functional data analyses.
<i> Medicine and Science in Sports and Exercise, </i>
<b>48</b> 1723-1729.
[[Link](http://journals.lww.com/acsm-msse/Abstract/2016/09000/New_Insights_into_Activity_Patterns_in_Children,.11.aspx)
| [PDF](Downloads/HeadStart.pdf)
| [Code](Downloads/HeadStartCode.zip)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/27183122)]

@@

Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, T. Ogden (2016).
Variable Selection in Function-on-Scalar Regression.
<i> Stat, </i>
<b>5</b> 88-101.
[[Link](http://onlinelibrary.wiley.com/doi/10.1002/sta4.106/abstract)
| [PDF](Downloads/FoS_VarSelect.pdf)
| Implemented in [refund](https://github.com/refunders/refund) as fosr.vs()]

**J. Goldsmith**, T. Kitago (2016).
Assessing Systematic Effects of Stroke on Motor Control using Hierarchical Function-on-Scalar Regression.
<i> Journal of the Royal Statistical Society: Series C, </i>
<b>65</b> 215-236.
[[PDF](Downloads/BayesPFSR_Paper.pdf)
| [Link](http://onlinelibrary.wiley.com/doi/10.1111/rssc.12115/abstract)
| [Code](Downloads/BayesPFSR_Code.zip)
| [Shiny App](https://jeff-goldsmith.shinyapps.io/MotorControl_Interactive)]

@@

**J. Goldsmith**, V. Zipunnikov, J. Schrack (2015).
Generalized Multilevel Functional-on-Scalar Regression and Principal Component Analysis.
<i> Biometrics, </i>
<b>71</b> 344-353.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/biom.12278/abstract)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25620473)
| [Code](Downloads/GenMFPCA_Code.zip)
| [Shiny App](https://jeff-goldsmith.shinyapps.io/GFPCA_interactive)]

@@

**J. Goldsmith**, F. Scheipl (2014).
Estimator Selection and Combination in Scalar-on-Function Regression.
<i> Computational Statistics and Data Analysis, </i>
<b>70</b> 362-372.
[[Link](http://www.sciencedirect.com/science/article/pii/S0167947313003629) |
[PDF](Downloads/Ensembling_Paper.pdf) |
[Code](Downloads/Ensembling_Code.zip)]

@@

**J. Goldsmith**, C. M. Crainiceanu, B. S. Caffo, D. S. Reich (2012).
Longitudinal Penalized Functional Regression for Cognitive Outcomes on Neuronal Tract Measurements.
<i> Journal of the Royal Statistical Society: Series C, </i>
<b>61</b> 453-469.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/j.1467-9876.2011.01031.x/abstract) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22679339) |
[Simulation Code](Downloads/LPFR_Code.zip)]

@@

**J. Goldsmith**, J. Bobb, C. M. Crainiceanu, B. S. Caffo, D. S. Reich (2011).
Penalized Functional Regression.
<i> Journal of Computational and Graphical Statistics, </i>
<b>20</b> 830-851.
[[Link](http://www.tandfonline.com/doi/abs/10.1198/jcgs.2010.10007#.U1BzC16ft94) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22368438) |
[Simulation Code](Downloads/PFR_Code.zip)]

@@

**J. Goldsmith**, M. P. Wand, and C. M. Crainiceanu (2011).
Functional Regression via Variational Bayes.
<i> Electronic Journal of Statistics, </i>
<b>5</b> 572-602.
[[Link](http://projecteuclid.org/euclid.ejs/1308143123) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22163061) |
[Simulation Code](Downloads/VB_Code.zip)]

@@

**J. Goldsmith**, L. Koss (2009).
Dynamical Properties of the Derivative of the Weierstrass Elliptic Function.
<i> Involve, </i>
<b>2</b> 267-288.
[[Link](http://msp.org/involve/2009/2-3/p02.xhtml) |
[pdf](Downloads/Weierstrass.pdf)]

>>>>

J. Lee<sup>&#8225;</sup>, G. Li, W. F. Christensen, G. Collins, M. Seeley, A. E. Bowden, D. T. Fullwood, and **J. Goldsmith** (2018+). 
Functional Data Analyses of Gait Data Measured Using In-Shoe Sensors. 
<i> Statistics in Biosciences, </i> 
accepted.

@@

D. Backenroth<sup>&#8225;</sup>, **J. Goldsmith**, M. D. Harran, J. C. Cortes, J. W. Krakauer, and T. Kitago (2018+).
Modeling motor learning using heteroskedastic functional principal components analysis.
<i> Journal of the American Statistical Association, </i> 
accepted.
[[PDF](resources/HetFCPA.pdf)]

@@

**J. Goldsmith**, X. Liu<sup>&#8225;</sup>, J. S. Jacobson, A. Rundle (2016).
New insights into activity patterns in children, found using functional data analyses.
<i> Medicine and Science in Sports and Exercise, </i>
<b>48</b> 1723-1729.
[[Link](http://journals.lww.com/acsm-msse/Abstract/2016/09000/New_Insights_into_Activity_Patterns_in_Children,.11.aspx)
| [PDF](resources/HeadStart.pdf)
| [Code](resources/HeadStartCode.zip)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/27183122)]

@@

Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, T. Ogden (2016).
Variable Selection in Function-on-Scalar Regression.
<i> Stat, </i>
<b>5</b> 88-101.
[[Link](http://onlinelibrary.wiley.com/doi/10.1002/sta4.106/abstract)
| [PDF](resources/FoS_VarSelect.pdf)
| Implemented in [refund](https://github.com/refunders/refund) as fosr.vs()]

**J. Goldsmith**, T. Kitago (2016).
Assessing Systematic Effects of Stroke on Motor Control using Hierarchical Function-on-Scalar Regression.
<i> Journal of the Royal Statistical Society: Series C, </i>
<b>65</b> 215-236.
[[PDF](resources/BayesPFSR_Paper.pdf)
| [Link](http://onlinelibrary.wiley.com/doi/10.1111/rssc.12115/abstract)
| [Code](resources/BayesPFSR_Code.zip)
| [Shiny App](https://jeff-goldsmith.shinyapps.io/MotorControl_Interactive)]

@@

**J. Goldsmith**, V. Zipunnikov, J. Schrack (2015).
Generalized Multilevel Functional-on-Scalar Regression and Principal Component Analysis.
<i> Biometrics, </i>
<b>71</b> 344-353.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/biom.12278/abstract)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25620473)
| [Code](resources/GenMFPCA_Code.zip)
| [Shiny App](https://jeff-goldsmith.shinyapps.io/GFPCA_interactive)]

@@

**J. Goldsmith**, F. Scheipl (2014).
Estimator Selection and Combination in Scalar-on-Function Regression.
<i> Computational Statistics and Data Analysis, </i>
<b>70</b> 362-372.
[[Link](http://www.sciencedirect.com/science/article/pii/S0167947313003629) |
[PDF](resources/Ensembling_Paper.pdf) |
[Code](resources/Ensembling_Code.zip)]

@@

**J. Goldsmith**, C. M. Crainiceanu, B. S. Caffo, D. S. Reich (2012).
Longitudinal Penalized Functional Regression for Cognitive Outcomes on Neuronal Tract Measurements.
<i> Journal of the Royal Statistical Society: Series C, </i>
<b>61</b> 453-469.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/j.1467-9876.2011.01031.x/abstract) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22679339) |
[Simulation Code](resources/LPFR_Code.zip)]

@@

**J. Goldsmith**, J. Bobb, C. M. Crainiceanu, B. S. Caffo, D. S. Reich (2011).
Penalized Functional Regression.
<i> Journal of Computational and Graphical Statistics, </i>
<b>20</b> 830-851.
[[Link](http://www.tandfonline.com/doi/abs/10.1198/jcgs.2010.10007#.U1BzC16ft94) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22368438) |
[Simulation Code](resources/PFR_Code.zip)]

@@

**J. Goldsmith**, M. P. Wand, and C. M. Crainiceanu (2011).
Functional Regression via Variational Bayes.
<i> Electronic Journal of Statistics, </i>
<b>5</b> 572-602.
[[Link](http://projecteuclid.org/euclid.ejs/1308143123) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22163061) |
[Simulation Code](resources/VB_Code.zip)]

@@

**J. Goldsmith**, L. Koss (2009).
Dynamical Properties of the Derivative of the Weierstrass Elliptic Function.
<i> Involve, </i>
<b>2</b> 267-288.
[[Link](http://msp.org/involve/2009/2-3/p02.xhtml) |
[pdf](resources/Weierstrass.pdf)]
